Sequential rank agreement methods for comparison of ranked lists

### 2015-04-24 latex/paper.Rnw
Initial changepoint analysis
Full lists

For the fully obseved list situation we can plot the sequantial
rank agreement \eqref{def:sra} as a function of depth $d$. If there is
a ... An example is seen in Figure~\ref{fig:example1}

@@

@@

\begin{figure}[tb]
\begin{center}
<<fig=TRUE,echo=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

@ %
\end{center}
 \label{fig:example1}
 \caption{Sequential rank agreement for 4 different analysis methods
   applied to the Golub data (thick red line). The red and blue shaded
 areas represent the pointwise 95\% normal areas for the XXX and XXY benchmarks,
respectively.}
\end{figure}

@@

<<>>=
library(changepoint)
cpt.mean(res)
cpt.mean(res2)
@

>>>>

For the fully obseved list situation we can plot the sequential rank
agreement \eqref{def:sra} as a function of depth $d$.  An example is
seen in Figure~\ref{fig:example1} where smaller values on the $y$ axis
correspond to better agreement among the lists than larger values. The
sequential rank agreement at depth $d$ can be interpreted as how many
ranks apart do we on average expect the items found until depth $d$ to
be.

If the lists generally agree on all items then we expect the
sequential rank agreement curve to be flat, but if there are changes
in the rank agreement levels then this suggests that there are changes
in the levels of agreement. In particular, we expect the agreement
among the lists to be better towards the top of the lists and worse
towards the end of the lists.

\texttt{FIXME: Skal der et specifikt eksempel ind her eller kan vi
  bare bruge det fra senere?}

@@

FIXME: For censored lists we expect a change point around the depth
where the lists are censored. This is an artefact stemming from the
fact that

@@

\begin{figure}[tb]
\begin{center}
<<fig=TRUE,echo=FALSE,width=3>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

@ %

<<fig=TRUE,echo=FALSE,width=3>>=
ysize <- 100
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@ %
\end{center}
 \caption{Sequential rank agreement for 4 different analysis methods
   applied to the Golub data (thick red line). The red and blue shaded
 areas represent the pointwise 95\% normal areas for the XXX and XXY benchmarks,
respectively.}
 \label{fig:example1}
\end{figure}

@@

<<>>=
library(changepoint)
cpt.mean(res, method="BinSeg")
cpt.mean(res2)
@
